An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
done with embedding proofs

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
  By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
  Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
  Therefore, $\risk{L}$ is polyhedral.

  The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$. 
  For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
  As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
  Repeat this process for every facet.
  Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
\end{proof}

Combining Proposition~\ref{prop:embed-risk-poly} with the straightforward result that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence: every polyhedral loss embeds some discrete loss.

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\jessie{We should move this proof to the Appendix, since all the props/lemmas it uses come after this point in the paper.}
\begin{proof}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lem:polyhedral-range-gamma}, \jessie{Referenced in next section} $\U = \Gamma(\simplex)$ is finite.
  For any $U \in \U$, let $\Gamma_U = \{p\in\simplex | \Gamma(p) = U\}$, which is nonempty by definition.
  Observe that for any $p\in\simplex$ and $u\in\reals^d$, we have $p \in \Gamma_u \iff u \in \Gamma(p) \iff U = \Gamma(p) \land u \in U \iff p\in\Gamma_U \land u \in U$.
  Thus, we have for all $u\in\reals^d$ that $\Gamma_u = \cup\{\Gamma_U | U\in\U,u\in U\}$.
  Now $\trim(\Gamma)$ \jessie{defined in the Appendix} is finite because the powerset of $\U$ is finite, and we apply Proposition~\ref{prop:embed-trim}, given in the Appendix.
\end{proof}

@@

We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear how to map the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
In this section, we show that separated link functions guarantee consistency, and give a construction to generate separated links for any polyhedral loss.
We illustrate our construction in the following section.

\raf{MOVE SOME PROPERTIES STUFF HERE?  E.g. Prop~\ref{prop:embed-trim}.}

\raf{Bo: this proves one of your lemmas}
\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there is a calibrated link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is calibrated.
\end{proof}

\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma := \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}

\begin{proposition}
  If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
\end{proposition}
\begin{proof}
  \raf{Use Hari's theorems from their section 8.}
\end{proof}

\begin{theorem}
  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
  Then there a separated link $\psi$ between $L$ and $\ell$.
\end{theorem}
\raft{Note: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.  This theorem would then not need the ``polyhedral'' part. This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}

Remark: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.  Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.  \raf{Is this true?}

@@

\raf{COOL THING TO POINT OUT: the prev two results show that when $L$ is polyhedral, then $\prop{L}$ has a finite range and so does its (multivalued map) inverse!}
\begin{theorem}\label{thm:general-duality-embedding}
  Let $\gamma:\simplex\toto\R$ be a non-redundant elicitable property, elicited by a loss whose Bayes risk is a closed function.
  Then $\gamma$ is embeddable.
  \raft{Low priority: what conditions on $L$ or $\gamma$ ensure that the Bayes risk is closed?}
\end{theorem}
\begin{proof}
  $G:\simplex\to\reals$ be the negative Bayes risk of the loss $L_\gamma$ eliciting $\gamma$, given by $G(p) = -\min_{r\in\R} \inprod{p}{L_\gamma(r)}$.
  Let $C:\reals^\Y\to\reals$ be the convex conjugate of $G$, given by $C(u) = \sup_{p\in\simplex} \inprod{p}{u} - G(p)$, which is finite on all of $\reals^\Y$ by~\citet[Corollary 13.3.1]{rockafellar1997convex} as $\dom\, G = \simplex$ is bounded.

  By~\citet[Theorem 2]{frongillo2014general} we know that for some $\D \subseteq \partial G(\simplex) \subseteq \reals^\Y$ we have a bijection $s : \R \to \D$ such that $\gamma(p) = s^{-1}(\D \cap \partial G(p))$.
  (In other words, $\gamma$ is a relabeling of subgradients of $G$.)
  Thus, we can write
  \begin{equation}
    \label{eq:1}
    r \in \gamma(p) \iff s(r) \in \partial G(p) \iff p \in \partial C(s(r))~,
  \end{equation}
  where the final equivalence follows from~\cite[Corollary 23.5.2]{rockafellar1997convex} as $G$ is a closed convex function.

  Now define $L:\reals^n\to\reals_+^\Y$ by $L(u) = C(u)\ones - u$, where $\ones\in\reals^\Y$ is the all-ones vector.
  \jessiet{Geometrically, what does this look like?  I'm imagining it as our tipping cost function, but I'm not sure on that.}
  We will show that $L$ embeds $\gamma$.
  As $L$ is convex, we may write the optimality condition as
  \begin{equation}
    \label{eq:2}
    u \in \prop{L}(p) \iff u \in \argmin_{u'} \inprod{p}{L(u')} \iff 0 \in \partial \inprod{p}{L(u)}~,
  \end{equation}
  where the subgradient $\partial$ is with respect to $u$.
  Plugging in our definition of $L$, we have
  \begin{align*}
    0 \in \partial \inprod{p}{L(u)}
    & \iff 0 \in \partial \inprod{p}{\left(C(u)\ones - u\right)}
    \\
    % & \iff 0 \in \partial \left(C(u) - p\cdot u\right)
    % \\
    & \iff 0 \in \partial C(u) - \{p\}
    \\
    & \iff p \in \partial C(u)~.
  \end{align*}
  \jessiet{Not sure I see this- REVISIT.}

  Together with eq.~\eqref{eq:1}, we now have for any $u \in \D$ and $p\in\simplex$ that
  \begin{equation}
    \label{eq:3}
    u \in \prop{L}(p) \iff p \in \partial C(u) \iff s^{-1}(u) \in \gamma(p)~.
  \end{equation}
  Recalling that $s$ is a bijection, we conclude that $L$ embeds $\gamma$ with embedding function $\varphi:\R\to\reals^\Y$ given by $\varphi(r) = s(r)$.

  We have now shown that $\gamma$ is $n$-embeddable.
  \jessiet{Notation question: is $C'(u';\ones)$ the directional derivative in the $\ones$ direction?}
  To drop a dimension, first note that $C$ is linear in the $\ones$ direction: for all $u'\in\reals^\Y$, the directional derivative $C'(u';\ones) = \sup_{p\in\partial C(u')} \inprod{p}{\ones} = 1$ as $\partial C(u')\subseteq\simplex$ for all $u'$; thus
  $C(u+\alpha\ones) = C(u) + \int_0^\alpha C'(u+\beta\ones;\ones) d\beta = C(u) + \alpha$.
  This linearity translates to invariance of $L$ in the direction of $\ones$:
  \begin{align*}
    L(u + \alpha\ones) = C(u+\alpha\ones)\ones - (u + \alpha\ones) = C(u)\ones + \alpha\ones - u - \alpha\ones = L(u)~.
  \end{align*}
  We now have for any $u\in\D$,
  \begin{align*}
    s^{-1}(u) \in \gamma(p) \iff u \in \prop{L}(p) \iff u - u_n\ones \in \prop{L}(p)\cap\R_2~.
  \end{align*}
  Letting $L':\reals^{n-1}\to\reals^\Y$ given by $L'(u') = L((u',0))$, and evoking Lemma~\ref{lem:loss-restrict}, we conclude $\prop{L'}(p) = \prop{L}\cap\R_2$ and thus $L'$ embeds $\gamma$ as well, with the embedding $\varphi(r) = (s(r)_1 - s(r)_n, \ldots, s(r)_{n-1} - s(r)_n)$.
  \jessiet{The notation $C'$ being a derivative kind of bothers me since $L'$ is used for another generic function... although I may just be misreading it or not familiar with standard notations.}
\end{proof}

>>>>

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.

% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.

%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$. 
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

Combining Proposition~\ref{prop:embed-risk-poly} with the straightforward result that polyhedral losses have polyhedral Bayes risks, we obtain the first direction of our equivalence between polyhedral losses and embedding.

\begin{lemma}
  \label{lem:poly-loss-poly-risk}
  If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
  By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
  For each $U\in \U$, select $u_U \in U$, and let $U' = \{u_U : U \in\U\}$.
  Then for all $p\in\simplex$ we have $\Gamma(p) \cap U' \neq \emptyset$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{U'}}$, which is polyhedral as $U'$ is finite.
  \raf{Yeah... so we didn't need Proposition~\ref{prop:embed-risk-poly} after all.  This already gives the discrete loss $L$ embeds!}
\end{proof}

\begin{theorem}\label{thm:poly-embeds-discrete}
  Every polyhedral loss $L$ embeds a discrete loss.
\end{theorem}
\begin{proof}
  We simply apply Lemma~\ref{lem:poly-loss-poly-risk} and Proposition~\ref{prop:embed-risk-poly}.
\end{proof}

@@

We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
We illustrate our construction in the following section.

\raf{Bo: this proves one of your lemmas}
\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there is a ``valid'' \raf{my scare quotes} link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
\end{proof}

\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}

\raft{COOL THING TO POINT OUT: when $L$ is polyhedral, then $\prop{L}$ has a finite range (this result) and so does its (multivalued map) inverse (trim result)!}

% \begin{proposition}
%   If $\psi$ is a separated link between losses $L$ and $\ell$, then $L$ and $\psi$ are consistenty with $\ell$. \jessie{Rephrase?}
% \end{proposition}
% \begin{proof}
%   \raf{Use Hari's theorems from their section 8.}
% \end{proof}

\begin{theorem}
  Let $L$ be polyhedral loss, and $\ell$ the discrete loss it embeds from Theorem~\ref{thm:poly-embeds-discrete}.
  Then there is link function $\psi$ such that $(L,\psi)$ is calibrated with respect to $\ell$.
\end{theorem}
\raft{FUTURE: we should comment in the discussion section that we probably can show that *any* loss embedding $\ell$ must be polyhedral-ish, meaning polyhedral except for stuff that is never optimal.  This theorem would then not need the ``polyhedral'' part. This is related to the ``convex envelope conjucture'', that if $L$ embeds $\ell$ via $\varphi$, you can just take the loss $L'$ such that $L_y$ is the convex envelope of points $\{(\varphi(r),L(r)_y)\}_{r\in\R}$.}
\raft{FUTURE: This prop and theorem give an excellent reason to focus on embeddings, since other techniques do not necessarily give you separated links for free.  Since we know we get them for free, we can just focus on the property, and study elicitation complexity; we know if we have a link at all it can be taken to be separated.  [[Is this true?]]}

@@
